j_play

### 2020-12-04 scripts/BCOR_combo.Rmd
Updated Data, Tidying, and Prevalence Calculations for ES

@@

@@

ESdata <- BCdatastripped %>% 
  filter(SPECIAL_NEEDS_CODE == "Chronic Health",
         DATA_LEVEL == "DISTRICT LEVEL",
         PUBLIC_OR_INDEPENDENT == "BC Public School",
         !DISTRICT_NUMBER %in% urban)  %>% 
  mutate(Public_population = BCpopulation$TOTAL_ENROLMENT[SCHOOL_YEAR-8],
         prevalence = NUMBER_OF_STUDENTS/Public_population) %>% 
  mutate(SCHOOL_YEAR = SCHOOL_YEAR+1995,
         pre16 = ifelse(SCHOOL_YEAR <= 2016, "before16", "after16")) %>%
  group_by(pre16) %>% 
  pivot_wider(
    names_from = pre16,
    values_from = prevalence
  )

>>>>

BCpop_district <- read_excel(here("data", "BCdistrictpop.xlsx")) %>% 
  select("SCHOOL_YEAR",
         "TOTAL_ENROLMENT",
         "DISTRICT_NUMBER") %>% 
  mutate(SCHOOL_YEAR = as.factor(SCHOOL_YEAR), 
         SCHOOL_YEAR = as.numeric(SCHOOL_YEAR)+8)

@@

BC_districtdata <- BCdatastripped %>% 
  filter(DATA_LEVEL == "DISTRICT LEVEL")
Prevalence_data <- inner_join(BCpop_district, BC_districtdata, by = c("SCHOOL_YEAR", "DISTRICT_NUMBER"), all.x = TRUE)

@@

ESdata <- Prevalence_data %>% 
  filter(SPECIAL_NEEDS_CODE == "Mild Behavioural Need",
         !DISTRICT_NUMBER %in% urban)  %>% 
  mutate(prevalence = NUMBER_OF_STUDENTS/TOTAL_ENROLMENT) %>% 
  mutate(SCHOOL_YEAR = SCHOOL_YEAR+1995,
         pre16 = ifelse(SCHOOL_YEAR <= 2016, "before16", "after16")) %>%
  group_by(pre16) %>% 
  pivot_wider(
    names_from = pre16,
    values_from = prevalence
  )

# 1) group_by for all students with SPED, then run that against public population to sort out overall prevelance of SPED
# 2)
